\textbf{The Illusion Game: A Novel Experimental Paradigm Provides Evidence in Favour of a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-09-20 submission/manuscript.Rmd
typo

Finally, we found that the sensitivity to illusions was positively associated with "positive" personality traits, such as *Agreeableness* and *Honesty-Humility*, and negatively associated with maladaptive traits such as *Antagonism*, *Psychoticism*, *Disinhibition* and *Negative Affect*. Beyond highlighting the relevance of illusions beyond the field of visual perception, these results point towards an association with high-level general-domain mechanisms. While the search for the exact mechanism(s) underlying these links is an important goal of future research, our findings unlock the potential of illusion-based tasks as sensitive tools to capture specific inter-individual neuro-cognitive differences.

>>>>

Finally, we found that the sensitivity to illusions was positively associated with "positive" personality traits, such as *Agreeableness* and *Honesty-Humility*, and negatively associated with maladaptive traits such as *Antagonism*, *Psychoticism*, *Disinhibition* and *Negative Affect*. Beyond highlighting the relevance of illusions beyond the field of visual perception, these results point towards an association with high-level domain-general mechanisms. While the search for the exact mechanism(s) underlying these links is an important goal of future research, our findings unlock the potential of illusion-based tasks as sensitive tools to capture specific inter-individual neuro-cognitive differences.
